
---
title: "Structural Topic Modelling- Final Version"
date: "April 2025"
output:
  html_document:
    theme: flatly
    highlight: tango
    toc: true
    toc_float: true
    number_sections: false

---

This file is used for running STM (Structural Topic modelling).

- dataset used and cleaned can be found on github
- based on earlier 4 colab files:

-- 01_txt_to_csv_and_merge.ipynb	
-- 02_add_continents_and_clean.ipynb	
-- 03_remove_french_translate.ipynb
-- 04_preprocessing_nlp.ipynb

This file uses "energy_clean.csv" which is the output of 04_preprocessing_nlp.ipynb.

# Download and Load Packages

```{r, warning=FALSE, message=FALSE, results='hide'}

library("quanteda") # Using quanteda as STM does not allow bigrams natively
library("stm")
library(textstem)  # for lemmatization

library(tidyverse)
library(dplyr)

library(stringi)
library(stringr)
library(stringdist)

library(igraph)
library(splines)
library(tm)
library(RColorBrewer)
library(stminsights)
library(ggplot2)

```

# Load the Data

```{r}

setwd("C:/Manjiri Satam_created/Hertie_study/Thesis/Final")

raw <- read.csv("energy_clean.csv", header = TRUE, stringsAsFactors = FALSE)

```

# Create a UID & remove unnecessary columns

```{r}

# UID 
raw <- raw %>%
  group_by(Year) %>%
  mutate(UID = str_c("P_", Year, "_", row_number())) %>%
  ungroup()

# remove columns not required

raw_clean <- raw %>% 
  select(Year, CrsID, ProjectTitle, SectorCode, LongDescription, ClimateMitigation, ClimateAdaptation, DonorName, RecipientName, RegionName, USD_Commitment, USD_Disbursement, USD_Received, LD_clean, UID) %>% 
  relocate(UID, .before = 1)



# Save as CSV
write_csv(raw_clean, "energy_clean_UID.csv")

```

# Quick Datachecks

Let's do some quick data checks before we proceed 

```{r}

#let's look at the data

head(raw_clean)
colnames(raw_clean)

```



```{r}
# Let's check the number of NAs in each column
sapply(raw_clean, function(x) sum(is.na(x)))

```

# EDA

## Projects per year

```{r}

#check how many projects are there per year

raw_clean %>% group_by(Year) %>% count() %>% ungroup()


```

```{r}
# plot projects per year

raw_clean %>% 
  group_by(Year) %>% 
  count() %>% 
  ggplot(aes(x = Year, y = n)) +
  geom_point() +
  geom_line(size = 1) +
  labs(title = "Count of Projects by Year",
       x = "Year",
       y = "Number of Projects") +
  theme_minimal()

```

## Sectorcode


```{r}

#check how many observations are there per in sectorcode

raw_clean %>% group_by(SectorCode) %>% count() %>% ungroup() %>% arrange(desc(n))

n_distinct(raw_clean$SectorCode)

```



```{r}
raw_clean %>% 
  group_by(Year, SectorCode) %>% 
  count() %>% 
  ggplot(aes(x = Year, y = n, color = as.factor(SectorCode))) +
  geom_line(size = 1) +
  labs(title = "Count of Projects by Year and SectorCode",
       x = "Year",
       y = "Number of Projects",
       color = "SectorCode") +
  theme_minimal()
```


## Climate Mitigation


```{r}

# mitigation

raw_clean %>% 
  count(ClimateMitigation) %>% 
  mutate(percent = round(100 * n / sum(n), 1)) %>% 
  arrange(desc(n))

```

```{r}

raw_clean %>% 
  group_by(Year, ClimateMitigation) %>% 
  count() %>% 
  ggplot(aes(x = Year, y = n, color = as.factor(ClimateMitigation))) +
  geom_line(size = 1) +
  labs(title = "Count of Projects by Year and ClimateMitigation",
       x = "Year",
       y = "Number of Projects",
       color = "ClimateMitigation") +
  theme_minimal()

```

## Climate Adaptation

```{r}

# adaptation - check how many observations are there 

raw_clean %>% 
  count(ClimateAdaptation) %>% 
  mutate(percent = round(100 * n / sum(n), 1)) %>% 
  arrange(desc(n))


```

```{r}

raw_clean %>% 
  group_by(Year, ClimateAdaptation) %>% 
  count() %>% 
  ggplot(aes(x = Year, y = n, color = as.factor(ClimateAdaptation))) +
  geom_line(size = 1) +
  labs(title = "Count of Projects by Year and ClimateAdaptation",
       x = "Year",
       y = "Number of Projects",
       color = "ClimateAdaptation") +
  theme_minimal()

```




## Recipient Region

```{r}

# Region 

#Geographical region of the recipient country/territory.

raw_clean %>% group_by(RegionName) %>% count() %>% ungroup() %>% arrange(desc(n))


```



```{r}

raw_clean %>% 
  group_by(Year, RegionName) %>% 
  count() %>% 
  ggplot(aes(x = Year, y = n, color = as.factor(RegionName))) +
  geom_line(size = 1) +
  labs(title = "Count of Projects by Year and Recipient_Region",
       x = "Year",
       y = "Number of Projects",
       color = "Recipient_Region") +
  theme_minimal()

```

## USD

```{r}

raw_clean %>%
  group_by(Year) %>%
  summarise(
    Commitment = sum(USD_Commitment, na.rm = TRUE),
    Disbursement = sum(USD_Disbursement, na.rm = TRUE),
    Received = sum(USD_Received, na.rm = TRUE)
  ) %>%
  pivot_longer(cols = c(Commitment, Disbursement, Received),
               names_to = "Type",
               values_to = "USD") %>%
  ggplot(aes(x = Year, y = USD, color = Type)) +
  geom_line(size = 1) +
  geom_point() +
  labs(title = "Annual Financial Flows in Energy Projects",
       x = "Year",
       y = "USD (Total)",
       color = "Flow Type") +
  theme_minimal()

```

# Model Prep- Create Document Frequency Matrix (DFM)

```{r}
# lets make a different dataframe before we start the STM work

meta_info <- raw_clean

```


## Stemming/Lemmatization and Tokenization

Using quanteda as STM does not allow bigrams natively 
First, simple one-word tokens, then combine with frequently occurring bi-grams.


```{r}
library(textstem)   # Load early to use lemmatization

# Apply lemmatization directly to your cleaned column
meta_info$LD_lemma <- lemmatize_strings(meta_info$LD_clean)

# NOW remove textstem and its dependencies
detach("package:koRpus.lang.en", unload = TRUE, force = TRUE)
detach("package:koRpus", unload = TRUE, force = TRUE)
detach("package:textstem", unload = TRUE, force = TRUE)

# Then load quanteda
library(quanteda)
```


```{r}

# Create corpus
corpus_obj <- quanteda::corpus(meta_info, text_field = "LD_lemma")
docnames(corpus_obj) <- meta_info$UID

# Now tokenization and further steps
customStopwords = c('el', 'et', 'la', 'de', 'les','dans', 'ce', 'des', 'du',  'le','sur', 'par', "en", 'ii', "au", "mi", "eg", "otherwise", "iii","gr", "also","four","six","approximately", "thus","shall")


# Tokenize and remove custom stopwords
toks_clean_unigrams  <- tokens(corpus_obj, remove_punct = TRUE, remove_symbols = TRUE) %>%
  tokens_remove(pattern = phrase(customStopwords), valuetype = "fixed") %>% 
  tokens_keep(pattern = "^[a-zA-Z]{2,}$", valuetype = "regex") #Remove single-letter tokens (like 'a', 'l', etc.)


#helper function to identify A_B and B_A and just keep A_B
canonicalize_bigrams <- function(toks_bigram) {
  tokens(
    sapply(toks_bigram, function(x) {
      vapply(x, function(bi) {
        paste(sort(unlist(strsplit(bi, "_"))), collapse = "_")
      }, character(1))
    })
  )
}

# Create true bigrams- Remove repeated-word bigrams like "energy_energy"
toks_bigram <- tokens_ngrams(toks_clean_unigrams, n = 2) %>% 
  canonicalize_bigrams() %>%
  tokens_select(pattern = "\\b(\\w+)_\\1\\b",
                selection = "remove",
                valuetype = "regex")



# Build a clean DFM with only proper bigrams
dfm_bigram <- dfm(toks_bigram) 



dfm_bigram <- dfm_bigram %>%
  dfm_trim(min_termfreq = 50, termfreq_type = "count", 
           max_docfreq = 0.90, docfreq_type = "prop")


```

min_termfreq
- What it means: The minimum number of times a term (like a word or bigram) must appear across all documents to be kept.
- Increase the value: Only the most common terms will be kept; rarer terms will be removed.
- Decrease the value: More rare terms will be included, even those that appear just a few times.

termfreq_type = "count"
- What it means: the total number of times a term appears across all documents (not just how many documents it appears in).
- If this were "prop" instead, it would consider the proportion of documents that contain the term instead of the total count.

max_docfreq
- What it means: The maximum number of documents (as a proportion) in which a term can appear before it's considered too common and removed.
- Increase the value (e.g., 0.95 to 1): Fewer terms will be removed; even very common terms might be kept.
- Decrease the value (e.g., 0.95 to 0.8): More very common terms will be removed because they appear in too many documents.

docfreq_type = "prop"
- What it means: the proportion of documents that contain a term (e.g., 0.95 means 95% of documents).
- If this were "count", it would look at the raw number of documents instead of the proportion.


```{r}
docvars(dfm_bigram) <- meta_info
```

## Convert to STM format

```{r}
#Convert to STM format
dfm_stm <- quanteda::convert(dfm_bigram, to = c("stm"),docvars=docvars(dfm_bigram))


#output will have object meta, documents, and vocab
dfm_stm$meta$Year <- as.numeric(dfm_stm$meta$Year)

docs <- dfm_stm$documents
vocab <- dfm_stm$vocab
meta <-dfm_stm$meta

```

# STM Model (Multiple Topics)

```{r}

#convert some variables as factors

factor_vars <- c("SectorCode", "ClimateMitigation", "ClimateAdaptation","DonorName", "RecipientName", "RegionName")

meta[factor_vars] <- lapply(meta[factor_vars], as.factor)


```

Number of topics from (10, 15, 20, 25, 35)

```{r}

multi_k_model <- manyTopics(docs,
                            vocab,
                            data=meta,
                            K=c(10, 15, 20, 25, 35),
                            runs = 2,
                            prevalence =~ bs(as.numeric(Year), df=5) + 
                              ClimateMitigation + ClimateAdaptation + RegionName,
                            init.type = "LDA",
                            seed=42,
                            max.em.its=10,
                            control = list(alpha = 0.5, eta = 0.1))
 

saveRDS(multi_k_model, "multi_k_model.rds")
 
read_rds("multi_k_model.rds")

```

Exclusivity: Measures how unique the top words of a topic are (i.e. not shared across topics)
Range: ~9.5 to 10+ is typical and good.

Semantic Coherence: Measures how coherent the top words are when seen together in the same documents.
Less negative = better.
Values range widely depending on corpus size, preprocessing, etc.

## Plot Multiple K Model


```{r}

 modelDetails = data.frame(
   K = numeric(),
   coherence = numeric(),
   exclusivity = numeric())

```


```{r}
modelDetails <- data.frame()

for (i in 1:length(multi_k_model$out)) {
  if (!is.null(multi_k_model$semcoh[[i]]) && !is.null(multi_k_model$exclusivity[[i]])) {
    modi <- data.frame(
      coherence = multi_k_model$semcoh[[i]],
      exclusivity = multi_k_model$exclusivity[[i]],
      K = multi_k_model$out[[i]]$settings$dim$K
    )
    modelDetails <- rbind(modelDetails, modi)
    
    cat(K, 
        " - Exclusivity:", mean(modi$exclusivity, na.rm=TRUE),
        " - Semantic Coherence:", mean(modi$coherence, na.rm=TRUE),
        "\n")
  }
}
```

```{r}
final_model_plot <- ggplot(modelDetails, aes(x = exclusivity, y = coherence, color = factor(K))) +
  geom_point(size = 2.5, alpha = 0.8) +  # smaller, cleaner dots
  scale_color_manual(values = c("red", "darkorange", "darkblue", "darkmagenta", "forestgreen")) + 
  theme_minimal(base_size = 12) +  # remove grey background
  labs(
    title = "Semantic Coherence vs Exclusivity by Number of Topics (K)",
    x = "Exclusivity",
    y = "Semantic Coherence",
    color = "Number of Topics (K)"
  ) +
  theme(
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
    legend.title = element_text(face = "bold"),
    plot.background = element_rect(fill = "white", color = NA),
    panel.background = element_rect(fill = "white", color = NA),
    panel.grid.major.y = element_line(color = "grey80"),
    panel.grid.major.x = element_line(color = "grey80"),
    panel.grid.minor = element_blank(),
    axis.text.y = element_text(size = 10, color = "black", margin = margin(r = 5)),
    axis.text.x = element_text(color = "black"),
    axis.title.x = element_text(color = "black"),
    legend.position = "bottom",
    legend.box = "horizontal"
  )

# Save in A4 ratio (recommended: 8 x 6 inches for clean inclusion)
ggsave("model_selection_coherence_exclusivity.png", final_model_plot, width = 8, height = 6, dpi = 300)

# Also display
final_model_plot

```

# STM K = 20 topics


```{r}


model_20_eng <- stm(docs, 
                vocab, 
                data=meta, 
                K=20,
                prevalence =~ bs(as.numeric(Year), df=5) +
                              ClimateMitigation + ClimateAdaptation + RegionName,
                init.type = "LDA", 
                seed=123, 
                max.em.its=25,
                control = list(alpha = 0.5, eta = 0.1)) 


```


```{r}

saveRDS(model_20_eng, "model_20_eng.rds")

read_rds("model_20_eng.rds")

```


# Interpret the model



```{r}

#Print top words for all topics

topic_labels <- labelTopics(model_20_eng, topics = c(1:model_20_eng$settings$dim$K), n=15)

topic_labels

```


save the above in a csv

```{r}

# Convert to tidy format
labels_tidy <- map_dfr(
  .x = c("prob", "frex", "lift", "score"),
  .f = function(metric) {
    tibble(
      Topic = 1:nrow(topic_labels[[metric]]),
      Metric = metric,
      Words = apply(topic_labels[[metric]], 1, paste, collapse = ", ")
    )
  }
)

# View or save
print(labels_tidy)

# Save as CSV
write_csv(labels_tidy, "topic_labels_20_eng.csv")

```

topic proportions per document

```{r}
# Assuming your model is called model20
theta_matrix <- model_20_eng$theta  # theta is a document-topic matrix

# Add document IDs if you have them, or use row numbers
doc_ids <- meta$UID 

# Combine into a data frame
doc_topic_df <- as.data.frame(theta_matrix)
doc_topic_df <- cbind(id = doc_ids, doc_topic_df)

# Optional: Rename columns
colnames(doc_topic_df)[-1] <- paste0("Topic", 1:ncol(theta_matrix))

# Save as CSV
write.csv(doc_topic_df, "doc_topic_distribution_20_eng.csv", row.names = FALSE)

# Preview
head(doc_topic_df)
```

# Create a Topic Name and Theme Lookup Table

```{r}

topic_names_theme <- tribble(
  
  ~Topic, ~Name, ~Theme,
  
   1, "Climate Programs", "Sustainable Transition",
   2, "Energy Access", "Access & Equity",
   3, "Indigenous Energy", "Access & Equity",
   4, "Performance Monitoring", "Monitoring & Technical Assistance",
   5, "IDB Projects", "Finance & Institutions",
   6, "Grid Infrastucture", "Infrastructure & Energy Systems",
   7, "Solar Access", "Access & Equity",
   8, "Capacity Deployment", "Monitoring & Technical Assistance",
   9, "Donor Reporting", "Finance & Institutions",
  10, "Geothermal Energy", "Infrastructure & Energy Systems",
  11, "Nuclear Disarmament", "Nuclear Disarmament",
  12, "Climate Finance Tools", "Finance & Institutions",
  13, "National Energy Support", "Monitoring & Technical Assistance",
  14, "Electricity Networks", "Infrastructure & Energy Systems",
  15, "Electrification Loans", "Finance & Institutions",
  16, "Thermal & Hydro Plants", "Infrastructure & Energy Systems",
  17, "Nuclear Safeguards", "Monitoring & Technical Assistance",
  18, "Green Funds", "Finance & Institutions",
  19, "Wind & Solar", "Sustainable Transition",
  20, "Power Subsector Mapping", "Infrastructure & Energy Systems"
)

```

```{r}
topic_names_theme$Topic <- as.character(topic_names_theme$Topic)
```

## theme colors

```{r}
theme_colors <- c(
  "Infrastructure & Energy Systems" = "darkblue",
  "Finance & Institutions" = "red",
  "Monitoring & Technical Assistance" = "darkorange",
  "Access & Equity" = "purple4",
  "Sustainable Transition" = "darkgreen",
  "Nuclear Disarmament" = "chocolate4"
)
```


## Correlation Matrix

```{r fig.width=8, fig.height=6, dpi=300}}

#estimates a correlation network between topics

mod.out.corr <- topicCorr(model_20_eng)

cor_matrix <- mod.out.corr$cor

rownames(cor_matrix) <- topic_names_theme$Name
colnames(cor_matrix) <- topic_names_theme$Name


# Save as high-res PNG
png("correlation_matrix.png", width = 8, height = 6, units = "in", res = 300)

corrplot::corrplot(cor_matrix,
                   tl.col = "black", # Topic label color
                   tl.cex = 0.5,     # control label size
                   col = colorRampPalette(c("darkblue", "white", "darkorange"))(200), # 200 intermediate color steps
                   tl.srt = 45,              # Rotate labels 45 degrees
                   addgrid.col = "grey",     # grid color
                   cl.cex = 0.7,             # legend size (color legend bar)
                   cl.align.text = "l",      # align colorbar text left
                   cl.ratio = 0.2)           # make legend (colorbar) thinner
dev.off()

```


## Semantic Coherence and Exclusivity

Semantic Coherence: Measures how often top words in a topic co-occur in documents. Higher (less negative) is better.

Exclusivity: Measures how unique the top words are to a single topic (not shared across many). Higher is better.

```{r}
# Compute semantic coherence
semcoh_scores <- semanticCoherence(model = model_20_eng, documents = docs)
semcoh_scores

# Compute exclusivity
exclusivity_scores <- exclusivity(model_20_eng)
exclusivity_scores
```

```{r}

# Combine for quick comparison
scores_df <- data.frame(
  Topic = 1:model_20_eng$settings$dim$K,
  SemanticCoherence = semcoh_scores,
  Exclusivity = exclusivity_scores
)

# Merge topic names and themes
scores_df$TopicName <- topic_names_theme$Name
scores_df$Theme <- topic_names_theme$Theme

# visualize

png("topic_quality.png", width = 8, height = 6, units = "in", res = 300)

ggplot(scores_df, aes(x = SemanticCoherence, y = Exclusivity, label = TopicName)) +
  geom_point(color = "darkblue", size = 2) +
  geom_text_repel(size = 3, max.overlaps = Inf, force = 2) +
  #geom_text(nudge_y = 0.02, size = 3) +
  theme_minimal() +
  labs(title = "Topic Quality: Semantic Coherence vs Exclusivity",
       x = "Semantic Coherence",
       y = "Exclusivity") +
  theme(
    plot.title = element_text(hjust = 0.5, size = 12, face = "bold"),
    axis.title = element_text(size = 10),
    axis.text = element_text(size = 10)
  )

dev.off()
```


# Influence of Covariates

# Temporal Trend - Year

```{r}

prep_v2 <- estimateEffect(1:20 ~ bs(as.numeric(Year), df=5) +
                            ClimateMitigation + ClimateAdaptation + RegionName,
                       stmobj = model_20_eng,
                       metadata = meta,
                       documents = docs,
                       uncertainty = "Global")

```

```{r}

effects_v2_year <- get_effects(estimates = prep_v2, variable = 'Year', type = 'pointestimate')

```

Ridge Plot

```{r}
effects_v2_year <- effects_v2_year %>% 
  rename(Topic = topic)

year_effects <- effects_v2_year %>% 
  left_join(topic_names_theme, by = "Topic")
  
year_effects$value <- as.numeric(as.character(year_effects$value))
  
```

```{r}
library(ggridges)


# Generate the plot
ridge_plot <- ggplot(year_effects, 
                     aes(x = value, y = Name, height = proportion, fill = Theme)) +
  geom_density_ridges(
    stat = "identity",
    scale = 1,  
    rel_min_height = 0.0001,
    color = "white",
    size = 0.3,
    position = "identity"
  ) +
  geom_vline(xintercept = 2014:2023, color = "grey80", linetype = "dashed") +
  scale_fill_manual(values = theme_colors) +
  scale_x_continuous(breaks = 2014:2023, limits = c(2014, 2023)) +
  theme_minimal(base_size = 13) +
  labs(x = "Year", y = NULL, fill = "Themes") +
  theme(
    plot.background = element_rect(fill = "white", color = NA),
    panel.background = element_rect(fill = "white", color = NA),
    panel.grid.major.y = element_line(color = "grey80"),
    panel.grid.major.x = element_line(color = "grey80"),
    panel.grid.minor = element_blank(),
    axis.text.y = element_text(size = 10, color = "black", margin = margin(r = 5)),
    axis.text.x = element_text(color = "black"),
    axis.title.x = element_text(color = "black"),
    legend.position = "bottom",
    legend.box = "horizontal"
  )

# Save and open
ggsave("ridge_year_eff.png", ridge_plot, width = 12, height = 10, dpi = 300)
browseURL("ridge_year_eff.png")


```


## Regional Effect- RegionName

```{r}


prep_region <- estimateEffect(1:20 ~ RegionName,
                       stmobj = model_20_eng,
                       metadata = meta,
                       documents = docs,
                       uncertainty = "Global")

```


```{r}
effects_v2_region <- get_effects(estimates = prep_region, variable = 'RegionName', type ='pointestimate')
```

```{r}
effects_v2_region <- effects_v2_region %>% 
  rename(Topic = topic)
```


```{r}

region_effects <- effects_v2_region %>% 
  left_join(topic_names_theme, by = "Topic")
  
```

```{r}
# Average topic proportions by region

regional_avg <- region_effects %>%
  group_by(value, Name) %>%
  summarise(avg_prop = mean(proportion, na.rm = TRUE), .groups = "drop")

```

```{r}

# Global average topic proportions

global_avg <- region_effects %>%
  group_by(Name) %>%
  summarise(global_prop = mean(proportion, na.rm = TRUE), .groups = "drop")

```

```{r}
# Combine both for comparison

regional_comparison <- regional_avg %>%
  left_join(global_avg, by = "Name") %>%
  mutate(relative_difference = avg_prop - global_prop) %>% 
  filter(value != "Regional and Unspecified")

regional_comparison <- regional_comparison %>% 
  mutate(value = case_when(value %in% c("Caribbean & Central America") ~ "Carib, Central America", TRUE ~ value))

```

```{r}

top_bottom <- regional_comparison %>%
  group_by(value) %>%
  slice_max(order_by = relative_difference, n = 5, with_ties = FALSE) %>%
  bind_rows(
    regional_comparison %>%
      group_by(value) %>%
      slice_min(order_by = relative_difference, n = 5, with_ties = FALSE)
  ) %>%
  ungroup() %>%
  mutate(
    # combine Topic and Region as one factor to allow within-facet sorting
    Topic_in_region = paste(Name, value, sep = "___"),
    Topic_in_region = fct_reorder(Topic_in_region, relative_difference)
  )

top_bottom <- top_bottom %>%
  mutate(OverUnder = ifelse(relative_difference > 0, "Overrepresented", "Underrepresented"))

```


```{r, fig.height= 15, fig.width= 9}

library(ggforce)

region_topic_plot <- ggplot(top_bottom, 
                            aes(x = Topic_in_region,
                                  y = relative_difference,
                                  fill = OverUnder)) +
  
                      geom_col(show.legend = FALSE) +
  
                      coord_flip() +
  
                      facet_wrap_paginate(~value, scales = "free_y", ncol = 3, page = 1) +
  
                      scale_fill_manual(values = c("Overrepresented" = "darkorange", "Underrepresented" = "darkblue")) +
  
                      scale_x_discrete(labels = function(x) gsub("___.*", "", x)) +  # Remove region from label
                      labs(
                        title = "Topic Emphasis by Region",
                        subtitle = "Top 5 Overrepresented and Underrepresented Topics Relative to Global Average",
                        x = "Topic",
                        y = "← Underrepresented Overrepresented →"
                      ) +
                      theme_minimal(base_size = 12) +
                      theme(
                        strip.text = element_text(face = "bold", size = 8),
                        axis.text.y = element_text(size = 6, colour = "black"),
                        axis.text.x = element_text(size = 6, colour = "black"),
                        plot.title = element_text(face = "bold", size = 14,hjust = 0.5),
                        plot.subtitle = element_text(size = 11),
                        plot.margin = margin(10, 15, 10, 10),
                        
                        plot.background = element_rect(fill = "white", color = NA),
                        panel.background = element_rect(fill = "white", color = NA),
                        panel.grid.major = element_line(color = "grey90"),
                        panel.grid.minor = element_blank()
                      )


# Save and open
ggsave("region_eff_topic_bar.png", region_topic_plot, width = 8, height = 8, dpi = 300)
browseURL("region_eff_topic_bar.png")


```


## Climate Mitigation


```{r}
prep_mitigation_v2 <- estimateEffect(1:20 ~ ClimateMitigation,
                       stmobj = model_20_eng,
                       metadata = meta,
                       documents = docs,
                       uncertainty = "Global")
```



```{r}
effects_v2_miti <- get_effects(estimates = prep_mitigation_v2, 
                               variable = 'ClimateMitigation', 
                               type = 'pointestimate')
```



```{r}
effects_miti_diff <- get_effects(estimates = prep_mitigation_v2,
                                 variable = "ClimateMitigation",
                                 type = "difference",
                                 cov_val1 = 1,  # Significant
                                 cov_val2 = 2,) # principal

```


```{r}
effects_v2_miti <- effects_v2_miti %>% 
  rename(Topic = topic)
```

```{r}
# Filter out 'Not Targeted' (value == 0)
miti_filtered <- mitigation_effects %>%
  filter(value %in% c(1, 2)) %>%
  mutate(value = factor(value, labels = c("Significant", "Principal")))
```


```{r}
# Plot
ggplot(miti_filtered, aes(x = proportion, y = Name, color = value)) +
  geom_point(size = 2) +
  geom_errorbarh(aes(xmin = lower, xmax = upper), height = 0.2) +
  scale_color_manual(values = c("darkorange", "forestgreen")) +
  labs(
    title = "Effect of Climate Mitigation (Significant & Principal)",
    x = "Expected Topic Proportion",
    y = NULL,
    color = "Mitigation Level"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    axis.text.y = element_text(size = 9),
    plot.title = element_text(size = 14, face = "bold"),
    legend.position = "bottom"
  ) +
  theme(
        strip.text = element_text(face = "bold", size = 13),
        axis.text.y = element_text(size = 10),
        plot.title = element_text(face = "bold", size = 14),
        plot.subtitle = element_text(size = 11),
        plot.margin = margin(10, 15, 10, 10),
                        
        plot.background = element_rect(fill = "white", color = NA),
        panel.background = element_rect(fill = "white", color = NA),
        panel.grid.major = element_line(color = "grey90"),
        panel.grid.minor = element_blank()
        )

# Save and open
ggsave("miti_eff_separate.png")


```


```{r}

# Start PNG device
png("climate_mitigation_diff_plot.png", width = 1200, height = 800, res = 150)

# Plot

plot.estimateEffect(prep_mitigation_v2,
    covariate = "ClimateMitigation",
    method = "difference",
    cov.value1 = 1,  # Significant
    cov.value2 = 2,  # Principal
    topics = 1:20,
    model = model_20_eng,
    labeltype = "custom",
    custom.labels = topic_names$Name,
    add = FALSE,
    xlab = "More Emphasis in Principal (→) vs Significant (←)",
    main = "Difference in Topic Proportions: Climate Mitigation Principal vs Significant",
    xlim = c(-0.08, 0.08),
    cex = 0.6)+
  theme(
        plot.background = element_rect(fill = "white", color = NA),
        panel.background = element_rect(fill = "white", color = NA),
        panel.grid.major = element_line(color = "grey90"),
        panel.grid.minor = element_blank()
        ) +
  

# Close the graphics device
dev.off()


```


```{r}

miti_diff <- mitigation_effects %>%
  select(Name, Theme, value, proportion) %>%
  filter(value %in% c(1, 2)) %>%
  mutate(value = factor(value, labels = c("Significant", "Principal"))) %>% 
  pivot_wider(names_from = value, values_from = proportion) %>%
  mutate(
    diff =  Significant - Principal  # Significant minus Principal  
  )


# Order topics by difference
miti_diff$Name <- factor(miti_diff$Name, levels = miti_diff$Name[order(miti_diff$diff)])


# Plot
miti_eff_arrow <- ggplot(miti_diff, aes(x = 0, xend = diff, y = Name, yend = Name, color = Theme)) +
  geom_segment(arrow = arrow(length = unit(0.15, "cm")), size = 1) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  scale_color_manual(values = theme_colors) +
  labs(
    title = "Difference in Topic Proportions (Significant - Principal)",
    x = "Topic Proportion Difference",
    y = NULL,
    color = "Theme"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    axis.text.y = element_text(size = 9),
    plot.title = element_text(face = "bold"),
    legend.position = "bottom",
                        
    plot.background = element_rect(fill = "white", color = NA),
    panel.background = element_rect(fill = "white", color = NA),
    panel.grid.major = element_line(color = "grey90"),
    panel.grid.minor = element_blank()
    )


# Save and open
ggsave("miti_eff_arrow.png", miti_eff_arrow)
browseURL("miti_eff_arrow.png")

```

Positive values (right of zero) → Topic is more emphasized in  Significant (1) mitigation projects

Negative values (left of zero) → Topic is more emphasized in Principal (2) mitigation projects



## Climate Adaptation


```{r}
prep_adap_v2 <- estimateEffect(1:20 ~ ClimateAdaptation,
                       stmobj = model_20_eng,
                       metadata = meta,
                       documents = docs,
                       uncertainty = "Global")
```



```{r}
effects_v2_adap <- get_effects(estimates = prep_adap_v2, 
                               variable = 'ClimateAdaptation', 
                               type = 'pointestimate')
```

```{r}
effects_v2_adap <- effects_v2_adap %>% 
  rename(Topic = topic)
```


```{r}

adaptation_effects <- effects_v2_adap %>% 
  left_join(topic_names, by = "Topic") 
```


```{r}
# Filter out 'Not Targeted' (value == 0)
adap_filtered <- adaptation_effects %>%
  filter(value %in% c(1, 2)) %>%
  mutate(value = factor(value, labels = c("Significant", "Principal")))

# Plot
adap_eff_separate <- ggplot(adap_filtered, aes(x = proportion, y = Name, color = value)) +
  geom_point(size = 2) +
  geom_errorbarh(aes(xmin = lower, xmax = upper), height = 0.2) +
  scale_color_manual(values = c("darkorange", "forestgreen")) +
  labs(
    title = "Effect of Climate Adaptation (Significant & Principal) ",
    x = "Expected Topic Proportion",
    y = NULL,
    color = "Adaptation Level"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    axis.text.y = element_text(size = 9),
    plot.title = element_text(size = 14, face = "bold"),
    legend.position = "bottom",
    
    plot.background = element_rect(fill = "white", color = NA),
    panel.background = element_rect(fill = "white", color = NA),
    panel.grid.major = element_line(color = "grey90"),
    panel.grid.minor = element_blank()
  )


# Save and open
ggsave("adap_eff_separate.png", adap_eff_separate)
browseURL("adap_eff_separate.png")


```



```{r}

# Start PNG device
png("climate_adaptation_diff_plot.png", width = 1200, height = 800, res = 150)

# Plot

plot.estimateEffect(prep_adap_v2,
    covariate = "ClimateAdaptation",
    method = "difference",
    cov.value1 = 1,  # Significant
    cov.value2 = 2,  # Principal
    topics = 1:20,
    model = model_20_eng,
    labeltype = "custom",
    custom.labels = topic_names$Name,
    add = FALSE,
    xlab = "More Emphasis in Principal (→) vs Significant (←)",
    main = "Difference in Topic Proportions: Climate Adaptation Principal vs Significant",
    xlim = c(-0.08, 0.08),
    cex = 0.6) 

# Close the graphics device
dev.off()
  
```


```{r}

adap_diff <- adaptation_effects %>%
  select(Name, Theme, value, proportion) %>%
  filter(value %in% c(1, 2)) %>%
  mutate(value = factor(value, labels = c("Significant", "Principal"))) %>% 
  pivot_wider(names_from = value, values_from = proportion) %>%
  mutate(
    diff =  Significant - Principal  # Significant minus Principal  
  )


# Order topics by difference
adap_diff$Name <- factor(adap_diff$Name, levels = adap_diff$Name[order(adap_diff$diff)])


# Plot
adap_eff_arrow <- ggplot(adap_diff, aes(x = 0, xend = diff, y = Name, yend = Name, color = Theme)) +
  geom_segment(arrow = arrow(length = unit(0.15, "cm")), size = 1) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  scale_color_manual(values = theme_colors) +
  labs(
    title = "Difference in Topic Proportions (Significant - Principal)",
    x = "Topic Proportion Difference",
    y = NULL,
    color = "Theme"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    axis.text.y = element_text(size = 9),
    plot.title = element_text(face = "bold"),
    legend.position = "bottom",
    plot.background = element_rect(fill = "white", color = NA),
    panel.background = element_rect(fill = "white", color = NA),
    panel.grid.major = element_line(color = "grey90"),
    panel.grid.minor = element_blank()
  )


# Save and open
ggsave("adap_eff_arrow.png", adap_eff_arrow)
browseURL("adap_eff_arrow.png")

```


Positive values (right of zero) → Topic is more emphasized in  Significant (1) mitigation projects

Negative values (left of zero) → Topic is more emphasized in Principal (2) mitigation projects


## Mitigation & Adaptation Together

```{r}

effects_miti_diff <- get_effects(estimates = prep_mitigation_v2,
                                 variable = "ClimateMitigation",
                                 type = "difference",
                                 cov_val1 = 1,  # Significant
                                 cov_val2 = 2,) # principal

effects_adap_diff <- get_effects(estimates = prep_adap_v2,
                                 variable = "ClimateAdaptation",
                                 type = "difference",
                                 cov_val1 = 1,  # Significant
                                 cov_val2 = 2,) # principal
```


```{r}

effects_miti_diff <- effects_miti_diff %>% 
  rename(miti_diff = difference, miti_lower = lower, miti_upper = upper)

effects_adap_diff <- effects_adap_diff %>% 
  rename(adap_diff = difference, adap_lower = lower, adap_upper = upper)

```

```{r}

both_diff <- effects_miti_diff %>% 
  left_join(effects_adap_diff, by="topic")

both_diff <- both_diff %>% 
  rename(Topic = topic)

both_diff <- both_diff %>%
  mutate(Topic = as.character(Topic))

topic_names_theme <- topic_names_theme %>%
  mutate(Topic = as.character(Topic))

both_diff <- both_diff %>% 
  left_join(topic_names_theme, by="Topic")

```


```{r}
both_diff_long <- both_diff %>%
  pivot_longer(
    cols = c(miti_diff, adap_diff),
    names_to = "Type",
    values_to = "Estimate"
  ) %>%
  mutate(
    Lower = case_when(
      Type == "miti_diff" ~ miti_lower,
      Type == "adap_diff" ~ adap_lower
    ),
    Upper = case_when(
      Type == "miti_diff" ~ miti_upper,
      Type == "adap_diff" ~ adap_upper
    ),
    Type = ifelse(Type == "miti_diff", "Mitigation", "Adaptation")
  ) %>%
  select(Topic, Name, Type, Estimate, Lower, Upper, Theme)

both_diff_long <- both_diff_long %>%
  mutate(Theme = as.character(Theme)) %>%
  mutate(Theme = factor(Theme, levels = names(theme_colors)))
```


```{r}
# 2. Plot one graph, faceted
final_plot <- ggplot(both_diff_long, aes(x = Estimate, y = reorder(Name, Estimate), color = Theme)) +
  geom_point() +
  
  geom_errorbarh(aes(xmin = Lower, xmax = Upper), height = 0.2) +
  
  geom_vline(xintercept = 0, linetype = "dashed") +
  
  facet_wrap(~Type, ncol = 2, scales = "free_x") +  # two panels, separate x-axis
  
  labs(
    x = NULL,
    y = NULL,
    title = "Difference in Topic Prevalence for Climate Markers",
    subtitle = "With a 0.95 confidence intervals",
    caption = "Positive values: more Significant Marker, Negative values: more Principal Marker",
  ) +
  scale_color_manual(values = theme_colors) +
  
  theme_minimal(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold"),
    plot.background = element_rect(fill = "white", color = NA),
    panel.background = element_rect(fill = "white", color = NA),
    panel.grid.minor = element_blank(),
    axis.text.y = element_text(size = 8, colour = "black"),
    axis.text.x = element_text(size = 8),
    plot.title = element_text(size = 14, hjust = 0.5),
    plot.subtitle = element_text(size = 10, hjust = 0.5),
    plot.caption = element_text(hjust = 0.5, size = 10),
    legend.position = "bottom",
    legend.box = "horizontal",
    legend.key.size = unit(0.5, "lines"),
    legend.text = element_text(size = 8),
    legend.title = element_text(size = 0),
    legend.spacing.y = unit(0.2, 'cm')
  )

ggsave("miti_adap_diff_single_plot_colour.png", final_plot, width = 8, height = 8, dpi = 300)

final_plot
```






